Performance Optimization of Service Chain \\for vCPE in Small Size Network \\with OpenFlow Switch

### 2017-02-26 netsoft_paper.tex
fix some typing error

@@

\section{System Description}
\subsection{Overview of Network Function}\label{ssec:desc_nfv_overview}
With the concept of SDN-enabled VNFs \cite{sdn-enabled} \cite{manage-nve}, SDN technology work not only for traffic steering but also as a part of network functions. In this idea, network functions have been achieved by the synergies between computer infrastructures(NFV) and network infrastructures(NFVI) \cite{nfv2014-v121}\cite{nfv2014-v111}\cite{nfv2015}, shown in Fig. \ref{fig:desc_nfv_overview}. The former is a VNF controller, mainly responsible for dealing with stateful processing. The latter is a SDN switch \cite{sp:openflow1.3}, used for stateless processing.

\subsubsection{Stateful Processing component (VNF controller in container)}
This component have to control the workflow, keep the state associated with the VNF, and provide interface for service providers or customers to configure and update the behavior of the stateless datapath processing component. We use SDN controller to implement the NFV controller and it’s worth noting that we use southbound APIs of SDN controller framework to handle the interface between the stateful and stateless component with OpenFlow protocol \cite{onf}, which was originally designed for this.

@@

\subsection{Service Deployment Model}
Different from some related works are discussed about virtualizing network functions located in PE devices \cite{vcpe-enhance}, we come up with a network function service deployment model, with architecture mentioned in Fig. \ref{fig:desc_nfv_overview}. Because computing infrastructures handles the algorithm and policies, and the generic network devices only do stateless processing, the customer just need to buy a general SDN switch at their home gateway and will have a different network function service by subscribing different the NFV controller through our vCPE platform.

@@

The infrastructure controller is a composed Docker management server with the ability to manage the Docker resources like containers and images \cite{seo2014}\cite{compare-vm-container}. The infrastructure doesn't handle the customer authentication or maintaining the state of running service, it just follows the request from the infrastructure orchestrator to create, delete, start, stop and inspect containers.

@@

VNF Controllers contains a SDN controller developed with ryu framework \cite{web:ryu} and a remote launcher module. The SDN controller does not have a remote launcher module to remotely execute a SDN controller. We built a light-weight server as a launcher module to resolve the remotely execution issue. The remote launcher module monitor the SDN controller process ID (PID) and properly kill the SDN controller process ID when on demand. When the infrastructure controller once create the container, the remote module will run up initially, waiting request from VNF Orchestrator. The details of SDN controller design will be presented at section \ref{sec:mft}.

@@

\subsubsection{QoS}
Quality of Service (QoS) are always used to control the traffic flows of a network and prevent the traffic to exceed the network capacity and cause traffic congestion. Therefore we implement the bandwidth management using meter which is defined within OpenFlow protocol 1.3 to set the limitation of the bandwidth.
Beside achieving network functions virtualization with SDN technology, we also make the network administrator manage and monitor a network more easily. As a result, we can offer the user the best network quality in the limited network resource without traffic congestion.
In this paper, our QoS integrates with a flow classification engine and offers the three ways of bandwidth management.

@@

\subsection{QoS}
QoS service is mainly for traffic control and we provide two management funtion for QoS service. We will introduce these three strategy first and then discuss the flow table order of QoS service in multiple table model.

@@

The concept of this option is shown in Fig. \ref{fig:mft_qos_rate_host}. In T0, Host 1 and Host 2 are not limited yet. Since host 2 takes up a lot of bandwidth from network in T0 to T1, the network administrator sets Host 2 rate-limited under 400 Kbps. When controller receive this request, marked as (a), it will create a new meter with meter id = 1 and bandwidth = 400 Kbps, and set the rule in the flow table with destination MAC address = MAC address of Host 1 and meter = 1. According to our flow table, it will limit the rate of the target host. Then the traffic from Host 2 will reduce and be limited with 400Kbps immediately. The similar situation also occurs to Host 1 in T2. The administrator chooses to set Host 1 under 600 Kbps, marked as (b), and then traffic from Host 1 will be limited with 600Kbps.

@@

When network administrator request to rate limit a certain application to a certain bandwidth, we will equally distribute the bandwidth to each connection of the application. The controller set all flows belong to the same application into the same meter, and modifying the bandwidth of meter to achive our goal. For instance, if there is an application and we can find out which flows belong to this application through the flow classification engine and we want to limit this application to 1000Kbps. As Figure. \ref{fig:mft_qos_rate_app}, in T0, we know there are 3 connections belong this application and we will set the bandwidth of meter to each link with 1000/3 = 333Kbps. In T2, there are more two connections added to this application and we will reset the bandwidth of meter to each links with 1000/5 = 200Kbps. In T2, there is a connection ended by this application, we will reset the bandwidth of meter to each links with 1000/4 = 250Kbps, therefore. Whereas, the sum of bandwidth from this application is always being 1000 Kbps. That is, the bandwidth will be dynamically adjusted.

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{./figures/mft_qos_rate_app}
\caption{Illustration of rate-limiting for a certain application.}
\label{fig:mft_qos_rate_app}
\end{figure}

@@

\subsection{Overall procedure of application identification}
In training phase, we generate some data needed by our proposed method.
In classifying phase, if a flow meet some requirement, we use the method based on inspecting DNS response to classify;
otherwise, we use supervised ML to classify.

\subsection{Procedure of Supervised ML in our system}
In training phase, the architecture is show in Fig. \ref{fig:class_training}.
Flow classification engine is to build classification model by training data from Trainer,
and update the model when new training data comes.
Trainer is to analyze traffic from mirror port to get flow attributes.
After Trainer finishes calculating flow attributes of a flow,
it gets ground truth of the flow from Scanner or App Meta Server to generate training data\cite{Iwai2016},
and sends training data to flow classification engine.
App Meta Server is to store mappings of 5-tuple and ground truth from Scanner, and accept queries from Trainer.
Scanner is to get mappings of 5-tuple and ground truth from OS\cite{app-awareness-sdn}.
In classifying phase, the architecture is shown in Fig. \ref{fig:class_classifying}.
Flow classification engine is to use flow attributes from Classifier and classification model to get a classification result,
and sends classification result to Classifier.
Classifier is to analyze traffic from mirror port to get flow attributes.
After Classifier finishes calculating flow attributes of a flow,
it use flow attributes to ask flow classification engine for classification result if needed.

@@

\subsection{Algorithms we adopted in supervised ML}
We use algorithms implemented by Weka, a famous open source ML tool developed at the University of Waikato.
We call Weka Java API to build classification model.
We use three algorithms, namely RandomSupSpace with RandomTree\cite{TinKamHo1998},
FilterClassifier with discretization and RandomTree, and RandomCommittee with RandomTree.

@@

\subsubsection{Accuracy matrices and results}
To evaluate accuracy, we used precision, recall and F-measure (also called F1 score),
as shown in Eq. (1), Eq. (2), and Eq. (3) \cite{muc4}. In each round in 10-fold cross validation,
we calculate precision and recall of each category to calculate F1 score of each category.
After ten rounds, we calculate average F1 score of each category in 10 rounds. Table I shows F1 score of each category in top 40 most popular applications in testing data set. Next, we calculate average F1 score of all categories in 10 rounds, and we get 0.9062. The result (Table. \ref{table:classification_result}) shows it achieved high accuracy, which makes QoS possible to do bandwidth control or distribution at application level.

>>>>

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\section{System Description}
\subsection{Overview of Network Function}\label{ssec:desc_nfv_overview}
With the concept of SDN-enabled VNFs \cite{sdn-enabled}, SDN technology work not only for traffic steering but also as a part of network functions. In this idea, network functions have been achieved by the synergies between computer and network infrastructures, shown in Fig. \ref{fig:desc_nfv_overview}. The former is a VNF controller, mainly responsible for dealing with stateful processing. The latter is a SDN switch, used for stateless processing.

\subsubsection{Stateful Processing component (VNF controller in container)}
This component have to control the workflow, keep the state associated with the VNF, and provide interface for service providers or customers to configure and update the behavior of the stateless datapath processing component. We use SDN controller to implement the NFV controller and it’s worth noting that we use southbound APIs of SDN controller framework to handle the interface between the stateful and stateless component with OpenFlow protocol, which was originally designed for this.

@@

\subsection{Service Deployment Model}
With architecture mentioned in Fig. \ref{fig:desc_nfv_overview}, we come up with a network function service deployment model. Because computing infrastructures handles the algorithm and policies, and the generic network devices only do stateless processing, the customer just need to buy a general SDN switch at their home gateway and will have a different network function service by subscribing different the NFV controller through our vCPE platform.

@@

The infrastructure controller is a composed Docker management server with the ability to manage the Docker resources like containers and images. The infrastructure doesn't handle the customer authentication or maintaining the state of running service, it just follows the request from the infrastructure orchestrator to create, delete, start, stop and inspect containers.

@@

VNF Controllers contains a SDN controller developed with ryu framework and a remote launcher module. The SDN controller does not have a remote launcher module to remotely execute a SDN controller. We built a light-weight server as a launcher module to resolve the remotely execution issue. The remote launcher module monitor the SDN controller process ID (PID) and properly kill the SDN controller process ID when on demand. When the infrastructure controller once create the container, the remote module will run up initially, waiting request from VNF Orchestrator. The details of SDN controller design will be presented at section \ref{sec:mft}.

@@

\subsubsection{QoS}
Quality of Service (QoS) are always used to control the traffic flows of a network and prevent the traffic to exceed the network capacity and cause traffic congestion. Therefore we implement the bandwidth management using meter which is defined within OpenFlow protocol 1.3 to set the limitation of the bandwidth.
Beside achieving network functions virtualization with SDN technology, we also make the network administrator manage and monitor a network more easily. As a result, we can offer the user the best network quality in the limited network resource without traffic congestion.
In this paper, our QoS integrates with a flow classification engine and offers the two ways of bandwidth management.

@@

\subsection{QoS}
QoS service is mainly for traffic control and we provide two management funtion for QoS service. We will introduce these two strategy first and then discuss the flow table order of QoS service in multiple table model.

@@

The concept of this option is shown in Fig. \ref{fig:mft_qos_rate_host}. In T0, Host 1 and Host 2 are not limited yet. Since Host 2 takes up a lot of bandwidth from network in T0 to T1, the network administrator sets Host 2 rate-limited under 400 Kbps. When controller receive this request, marked as (a), it will create a new meter with meter id = 1 and bandwidth = 400 Kbps, and set the rule in the flow table with destination MAC address = MAC address of Host 1 and meter = 1. According to our flow table, it will limit the rate of the target host. Then the traffic from Host 2 will reduce and be limited with 400Kbps immediately. The similar situation also occurs to Host 1 in T2. The administrator chooses to set Host 1 under 600 Kbps, marked as (b), and then traffic from Host 1 will be limited with 600Kbps.

@@

When network administrator request to rate limit a certain application to a certain bandwidth, we will equally distribute the bandwidth to each connection of the application. The controller set all flows belong to the same application into the same meter, and modifying the bandwidth of meter to achive our goal. For instance, if there is an application and we can find out which flows belong to this application through the flow classification engine and we want to limit this application to 1000Kbps. As Figure. \ref{fig:mft_qos_rate_app}, in T0, we know there are 3 connections belong this application and we will set the bandwidth of meter to each link with 1000/3 = 333Kbps. In T2, there are more two connections added to this application and we will reset the bandwidth of meter to each links with 1000/5 = 200Kbps. In T2, there is a connection ended by this application, we will reset the bandwidth of meter to each links with 1000/4 = 250Kbps, therefore. Whereas, the sum of bandwidth from this application is always being 1000 Kbps. That is, the bandwidth will be dynamically adjusted according the numbers of connections.

It is worth mentioning that we would not change any rules in flow table and we only change the bandwidth of the correspond meter in the meter table. Therefore, there only have a little overhead to switch and controller.
\begin{figure}[!t]
\centering
\includegraphics[width=3in]{./figures/mft_qos_rate_app}
\caption{Illustration of rate-limiting for a certain application.}
\label{fig:mft_qos_rate_app}
\end{figure}

@@

\subsection{Overall procedure of application identification}
In order to let QoS management system be able to control or distribute bandwidth at application level, we designed and implemented an application identification system (also called flow classification system) to judge each flow is established by what application. In other words, the application identification system can classify each flow as an application name in real time, rather than a rough category or a transport layer protocol. The corresponding application name of a flow means the name of the application which establishes the flow. We use supervised machine learning (ML) and a method based on inspecting domain name service (DNS) responses to do flow classification. The system analyzes the packets whose transport protocol are TCP or UDP. Except for DNS responses, the system only reads headers to get transport layer information of packets without inspecting their payload.

\subsection{Procedure of Supervised ML in our system}
In training phase, the architecture is show in Fig. \ref{fig:class_training}. Flow classification engine is to build classification model by training data from Trainer, and update the model when new training data comes. Trainer is to analyze traffic from mirror port to get flow attributes. After Trainer finishes calculating flow attributes of a flow, it gets ground truth of the flow from Scanner or App Meta Server to generate training data, and sends training data to flow classification engine. App Meta Server is to store mappings of 5-tuple and ground truth from Scanner, and accept queries from Trainer. Scanner is to get mappings of 5-tuple and ground truth from OS.
In classifying phase, the architecture is shown in Fig. \ref{fig:class_classifying}. Flow classification engine is to use flow attributes from Classifier and classification model to get a classification result, and sends classification result to Classifier. Classifier is to analyze traffic from mirror port to get flow attributes. After Classifier finishes calculating flow attributes of a flow, it use flow attributes to ask flow classification engine for classification result if needed.

@@

\subsection{Algorithms we adopted in supervised ML}
We use algorithms implemented by Weka, a famous open source ML tool developed at the University of Waikato. We call Weka Java API to build classification model. We use three algorithms, namely RandomSupSpace with RandomTree, FilterClassifier with discretization and RandomTree, and RandomCommittee with RandomTree.

@@

\subsubsection{Accuracy matrices and results}
To evaluate accuracy, we used precision, recall and F-measure (also called F1 score), as shown in Eq. (1), Eq. (2), and Eq. (3) []. In each round in 10-fold cross validation, we calculate precision and recall of each category to calculate F1 score of each category. After ten rounds, we calculate average F1 score of each category in 10 rounds. Table I shows F1 score of each category in top 40 most popular applications in testing data set. Next, we calculate average F1 score of all categories in 10 rounds, and we get 0.9062. The result (Table. \ref{table:classification_result}) shows it achieved high accuracy, which makes QoS possible to do bandwidth control or distribution at application level.
